Abstract Binding Trees

### 2015-10-21 paper.tex
Use \oint for grothendieck construction

@@

Let $\Symbols$ be an infinite set of symbols; let $\Finsets$ be the free
cocartesian category over $\Symbols\times\Sorts$. Then, fix a covariant presheaf of operators
$\Operators:\Finsets\times\Arities\to\Sets$ such that the arrows in $\Finsets$
lift to renamings of operators' parameters; via the Grothendieck construction,
we can also consider the set $\int\Operators$ of operators
$(U,\varrho,\vartheta)$ for $\Member{\vartheta}{\Operators(\Upsilon,\varrho)}$.

@@

Operators are defined by specifying the fibres of $\int\Operators$ in which
they reside. For instance, consider the lambda calculus with a single sort,
$\SortExp$; we give its signature by asserting the following about its
operators:
\begin{gather*}
  \IsOperator{\Upsilon}{\lambda}{
    \MkArity{\MkValence{\cdot}{\SortExp}{\SortExp}}{\SortExp}
  }\\
  \IsOperator{\Upsilon}{\mathsf{ap}}{
    \MkArity{
      \MkValence{\cdot}{\cdot}{\SortExp},
      \MkValence{\cdot}{\cdot}{\SortExp}
    }{\SortExp}
  }
\end{gather*}

>>>>

\newcommand\Grothendieck[1]{\oint #1}

@@

Let $\Symbols$ be an infinite set of symbols; let $\Finsets$ be the free
cocartesian category over $\Symbols\times\Sorts$. Then, fix a covariant
presheaf of operators $\Operators:\Finsets\times\Arities\to\Sets$ such that the
arrows in $\Finsets$ lift to renamings of operators' parameters; via the
Grothendieck construction, we can also consider the set $\Grothendieck\Operators$ of
operators $(\Upsilon,\varrho,\vartheta)$ for
$\Member{\vartheta}{\Operators(\Upsilon,\varrho)}$.

@@

Operators are defined by specifying the fibres of $\Grothendieck\Operators$ in which
they reside. For instance, consider the lambda calculus with a single sort,
$\SortExp$; we give its signature by asserting the following about its
operators:
\begin{gather*}
  \IsOperator{\Upsilon}{\lambda}{
    \MkArity{\MkValence{\cdot}{\SortExp}{\SortExp}}{\SortExp}
  }\\
  \IsOperator{\Upsilon}{\mathsf{ap}}{
    \MkArity{
      \MkValence{\cdot}{\cdot}{\SortExp},
      \MkValence{\cdot}{\cdot}{\SortExp}
    }{\SortExp}
  }
\end{gather*}
